### 2023-10-09 main.tex
fix

\textbf{Remark}: In case of $N=2$ we can introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, we call $\ell_{1},\ldots,\ell_{q}$ the coordinates where particles of type $1$ are present. Thus, the coefficient of the above formula can be written as

@@

=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=k+1}^{q}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}
Moreover, for each $q\in \{1,\ldots,L\}$ using the coordinates $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$, calling $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$ and, by varying $q$, we have a one-to-one mapping with $\bm{\tau}$. Therefore, we can write 

@@

\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Subsection \ref{subsectionSSHsec}. If we stop distinguishing types of non-empty particles we have that \eqref{ABS} reads
	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{L}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
	\\&\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)\dt
where $x_{k}$ denotes the position of the particle $k$ among $q$. For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
	\prod_{k=1}^{L}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)^{c_{k}}\dt
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{L}\left(L+2-x_{k}-\sum_{i=k}^{L}c_{i}\right)^{c_{k}}=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\left(L+2-\ell_{k}-(q-k+1)\right)\dt

@@

\Psi^{'}(\bm{\ell},q)=\sum_{q=0}^{L}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(L+1-\ell_{k}-q+k\right)}{(2+L-k)}\dt
where $\bm{\ell}=(\ell_{1},\ldots,\ell_{q})$. 

@@

\begin{comment} introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes

@@

>>>>

\textbf{Remark}: In case of $N=2$ we can introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, we for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. By varying $q$, we have a one-to-one mapping with $\bm{\tau}$. Thus, the coefficient of the above formula can be written as

@@

=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=x_{k}+1}^{L}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}\dt
Therefore, we can write 

@@

\textbf{Remark}: In the case of $N=2$ we can argue similarly as we did in the Remark of Subsection \ref{subsectionSSHsec}. If we stop distinguishing types of non-empty particles and by introducing $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x,1}}$ we have that \eqref{ABS} reads
	\Psi^{'}(\bm{\tau})=&\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\frac{\Gamma(L+2-q)}{\Gamma(L+2)}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}
	\\&\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}\dt
 For any fixed $q$ we must consider all possible values of $(c_{i})_{i\in\{1,\ldots,m\}}$ such that its sum is equal to $q$. For each of these $(c_{i})_{i\in\{1,\ldots,m\}}$ we add a term given by  
	\prod_{x=1}^{L}\left(L+2-x-\sum_{i=x}^{L}c_{i}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)
where $x_{k}$ is the position of the $k$-th particle among $q$. 
We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, thus we have that 
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt

@@

\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt

@@

 introducing $q=\sum_{j=1}^{m}c_{i}$ in the colour-blind situation \eqref{exactCorrelations} becomes

@@

All in all we have that
